Review on precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-04 manuscript.tex
importing from manubot : figures

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{https://media.springernature.com/lw685/springer-static/image/art\%3A10.1038\%2Fs41467-021-26175-1/MediaObjects/41467_2021_26175_Fig1_HTML.png}
\caption{a Spike raster for repeated presentations (N = 40) of a high-contrast (10\% Michelson contrast) drifting Gabor recorded from area MT of a fixating marmoset (stimulus-onset, red line; mean response, blue line). A single-trial LFP trace is plotted in gray, and the average LFP response is plotted in black. The relative power between baseline (−200 ms to stimulus-onset) and evoked fluctuations (stimulus-onset + 50--250 ms) significantly favored the evoked response (right panel; N = 110 trials; median = 1.89 dB, p = 0.000019, two-tailed Wilcoxon's ranked-sum test). b Same as in (a), but for a low contrast stimulus (\textless2\% Michelson contrast). The relative power between baseline and evoked LFP fluctuations was not statistically different from parity (median = 1.23 dB, p = 0.087 two-tailed Wilcoxon's ranked-sum test). c An example of spontaneous LFP fluctuations structured as a traveling wave recorded from a spatially distributed multielectrode array in marmoset area MT. d Histogram of spontaneous spike probability as a function of the generalized phase of the LFP during fixation. e The average evoked response to low contrast stimuli was stronger when a more excitable phase (±π rad) of a spontaneous traveling wave aligned with the retinotopic location of the target (aligned, green line) as compared to when a less excitable phase (0 rad) was aligned (unaligned, purple line; N = 43 wave and non-wave trials; shaded region SEM; p = 0.0000015 two-tailed Wilcoxon's rank-sum test). Data for panels c--e modified from Davis et al.17 with permission.}\label{fig:davis}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{https://www.pnas.org/cms/10.1073/pnas.1718518116/asset/ab9a48f6-b28f-40c1-978e-6f6dbec39b98/assets/graphic/pnas.1718518116fig01.jpeg}
\caption{Mixed distance and duration representation in CA1. (A) Calcium fluorescence (heatmap) of CA1 neurons participating to run sequences in consecutive imaging sessions. Cells have been selected and ordered with respect to their activity in the first imaging session (Top). The black line represents speed of the mouse.}\label{fig:haimerl}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{https://laurentperrinet.github.io/grant/anr-anr/event_driven_computations.png}
\caption{A miniature, event-based ATIS sensor. Contrary to a classical frame-based camera for which a full dense image representation is given at discrete, regularly spaced timings, the event-based camera provides with events at the micro-second resolution. These are sparse as they represent luminance increments or decrements (ON and OFF events, respectively).}\label{fig:silicon_retina}
\end{figure}

>>>>

\begin{figure}
\centering
%\includegraphics[width=1\textwidth,height=\textheight]{https://media.springernature.com/lw685/springer-static/image/art\%3A10.1038\%2Fs41467-021-26175-1/MediaObjects/41467_2021_26175_Fig1_HTML.png}
\caption{a Spike raster for repeated presentations (N = 40) of a high-contrast (10\% Michelson contrast) drifting Gabor recorded from area MT of a fixating marmoset (stimulus-onset, red line; mean response, blue line). A single-trial LFP trace is plotted in gray, and the average LFP response is plotted in black. The relative power between baseline (−200 ms to stimulus-onset) and evoked fluctuations (stimulus-onset + 50--250 ms) significantly favored the evoked response (right panel; N = 110 trials; median = 1.89 dB, p = 0.000019, two-tailed Wilcoxon's ranked-sum test). b Same as in (a), but for a low contrast stimulus (\textless2\% Michelson contrast). The relative power between baseline and evoked LFP fluctuations was not statistically different from parity (median = 1.23 dB, p = 0.087 two-tailed Wilcoxon's ranked-sum test). c An example of spontaneous LFP fluctuations structured as a traveling wave recorded from a spatially distributed multielectrode array in marmoset area MT. d Histogram of spontaneous spike probability as a function of the generalized phase of the LFP during fixation. e The average evoked response to low contrast stimuli was stronger when a more excitable phase (±π rad) of a spontaneous traveling wave aligned with the retinotopic location of the target (aligned, green line) as compared to when a less excitable phase (0 rad) was aligned (unaligned, purple line; N = 43 wave and non-wave trials; shaded region SEM; p = 0.0000015 two-tailed Wilcoxon's rank-sum test). Data for panels c--e modified from Davis et al.17 with permission.}\label{fig:davis}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics{https://www.pnas.org/cms/10.1073/pnas.1718518116/asset/ab9a48f6-b28f-40c1-978e-6f6dbec39b98/assets/graphic/pnas.1718518116fig01.jpeg}
\caption{Mixed distance and duration representation in CA1. (A) Calcium fluorescence (heatmap) of CA1 neurons participating to run sequences in consecutive imaging sessions. Cells have been selected and ordered with respect to their activity in the first imaging session (Top). The black line represents speed of the mouse.}\label{fig:haimerl}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/event_driven_computations.png}
\caption{A miniature, event-based ATIS sensor. Contrary to a classical frame-based camera for which a full dense image representation is given at discrete, regularly spaced timings, the event-based camera provides with events at the micro-second resolution. These are sparse as they represent luminance increments or decrements (ON and OFF events, respectively).}\label{fig:silicon_retina}
\end{figure}
